---
title: "Milestone 2"
author: "Shadae Peart, Jasmine Mingo"
date: "2026-10-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
## This dataset 

library(readr)

cdc_wonder_mortality <- read_csv("cdc_wonder_mortality.csv")
cdc_wonder_population <- read_csv("cdc_wonder_population.csv")
kff_cms_medicaid_state_summary <- read_csv("kff_cms_medicaid_state_summary.csv")
kff_cms_medicare_state_summary <- read_csv("kff_cms_medicare_state_summary.csv")
```






```



``` {r}
# Check variable names
names(cdc_wonder_mortality)
names(cdc_wonder_population)
names(kff_cms_medicaid_state_summary)
names(kff_cms_medicare_state_summary)

# Check data types
str(cdc_wonder_mortality)
str(cdc_wonder_population)
str(kff_cms_medicaid_state_summary)
str(kff_cms_medicare_state_summary)
```

```{R}
summary(cdc_wonder_mortality)
summary(cdc_wonder_population)
summary(kff_cms_medicaid_state_summary)
summary(kff_cms_medicare_state_summary)

mean(cdc_wonder_mortality$Deaths, na.rm = TRUE)
median(cdc_wonder_mortality$Deaths, na.rm = TRUE)
range(cdc_wonder_mortality$Deaths, na.rm = TRUE)
```
```{R}
unique(cdc_wonder_mortality$State)

length(unique(cdc_wonder_mortality$State))
```
```{R}
head(cdc_wonder_mortality)
knitr::kable(head(cdc_wonder_mortality))
```